---
title: "Strings and regex in R answers"
subtitle: "Maria Novosolov"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["default", "custom-fonts.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: '16:9'
      beforeInit: "https://platform.twitter.com/widgets.js"
---

```{r}
library(tidyverse)
```


---
  
  class: exercise

# Guess the regex

.center[.xlarge[any vowel]]

--
  
  .center[.xlarge[`[aeiou]`]]

---
  
  class: exercise

# Guess the regex

.center[.xlarge[starts with a capital letter]]

--
  
  .center[.xlarge[`^[A-Z]`]]

---
  
  class: exercise

# Guess the regex

.center[.xlarge[a vowel and the two characters next to it]]

--
  
  .center[.xlarge[`.[aeiou].`]]

---
  
  
  
  ---
  
  class: exercise

# Guess the regex

.center[.xlarge[at least one number]]

--
  
  .center[.xlarge[`[0-9]+`]]

---
  
  class: exercise

# Guess the regex

.center[.xlarge[ends with `jpg` or `jpeg`]]

--
  
  .center[.xlarge[`jp[e]{0,1}g`]]


---
  
  class: exercise

# Guess the regex

.center[.xlarge[at least 2 #s in a row]]
--
                  
.center[.xlarge[`[0-9]{2,}`]]

---

class: inverse, center, middle 
 
Some more practice
---
str_extract("It does not do to dwell on dreams and forget to live.", )

--
```{r}
str_extract("It does not do to dwell on dreams and forget to live.",
            "(?<=and )[A-z]+") #<<
```

---

str_extract("It does not do to dwell on dreams and forget to live.", )
--
```{r}
str_extract("It does not do to dwell on dreams and forget to live.",
            "[A-z]+(?= and)") #<<
```

                  